Summary Tables

### 2020-03-02 summary_tables_outcomes.Rmd
Reformat

@@

      el <- inner_join(el, td4, by = 'stage_mode')
    }
    print(kable(el, caption = city))
    td <- el
    names(td)[2:ncol(td)] <- paste(names(td)[2:ncol(td)], city, sep = "_")

>>>>

overall_el_normalized <- list()

@@

    el <- inner_join(el, td4, by = 'stage_mode')
  }

  el <- el %>% ungroup() %>% janitor::adorn_totals(c('row', 'col'))

  print(kable(el, caption = city))
  td <- el
  names(td)[2:ncol(td)] <- paste(names(td)[2:ncol(td)], city, sep = "_")

  overall_el_normalized[[city]] <- td
